Towards a Practical Face Recognition System: \\ Robust Alignment and Illumination by Sparse Representation

### 2011-04-05 faces_system.tex
Hacking to get spacing acceptable

% make the title area

@@

\IEEEdisplaynotcompsoctitleabstractindextext

@@

\begin{figure}
\centering \begin{tabular}{cc}
\includegraphics[height=1in]{figures_cvpr/promo/case1/detector.png}&
\hspace{3mm}
\includegraphics[height=1in]{figures_cvpr/promo/case1/sci_with_axis_face_case1.png}
\\ \includegraphics[height=1in]{figures_cvpr/promo/alignment_and_detector.png}&
\hspace{3mm}
\includegraphics[height=1in]{figures_cvpr/promo/case2/sci_with_axis_face_case2.png}
\\ \includegraphics[height=1in]{figures_cvpr/promo/case3/alignment.png} &
\hspace{3mm}
\includegraphics[height=1in]{figures_cvpr/promo/case3/sci_with_axis_face_case3.png}
\end{tabular} \caption{{\bf Effects of registration and illumination on
Recognition}. In this example we identify the girl among 20 subjects, by
computing the sparse representation of her input face with respect to the
entire training set. The absolute sum of the coefficients associated with each
subject is plotted on the right. We also show the faces reconstructed with each
subject's training images weighted by the associated sparse coefficients. The
red line (cross) corresponds to her true identity, subject 12. {\bf Top:} The
input face is from Viola and Jones' face detector (the black box) and all 38
illuminations specified in Section \ref{sec:illumination} are used in the
training.  {\bf Middle:} The input face is well-aligned (the white box) with
the training by our algorithm specified in Section \ref{sec:registration} but
only 24 frontal illuminations are used in the training for recognition (see
Section \ref{sec:illumination}). {\bf Bottom:} The input face is well aligned and
a sufficient set (all 38) of
illuminations are used in the training. Both are necessary for correct recognition
using SRC.}\label{fig:promo}
\vspace{-4mm}
\end{figure}
%\subsection{Compound Effect of Registration and Illumination}

Unfortunately, while the work \cite{Wright2009-PAMI} achieves impressive results, it does not deal with misalignment
between the test and training images, and it requires a rich set of illuminations
in the gallery images for good performance.
%Furthermore, the experiments were carried out on public datasets taken under
%controlled laboratory conditions such as Extended Yale B
%\cite{Georghiades2001-PAMI}, which do not contain realistic test images.
%two critical aspects of real world face recognition must be addressed:  significant variations in both the {\em image domain} and in
%the {\em image value}.
We illustrate the compounded effect of both alignment and illumination
with an example in Figure \ref{fig:promo}.
The task is to identify the girl among 20 subjects. If the test
face image, say obtained from an off-the-shelf face detector,
has even a small amount of registration error against the
training images (caused by mild pose, scale, or misalignment),
the sparse representation obtained using the method of \cite{Wright2009-PAMI} is no longer informative,
even if sufficient illuminations are present in the training, as shown in Figure
\ref{fig:promo}(top). Additionally, in order to span
the illuminations of a typical indoor (or outdoor) environment,
illuminations from behind the subject are needed in the
training set. Otherwise, even for perfectly aligned test images,
the sparse representation obtained using \cite{Wright2009-PAMI} will not necessarily be sparse or
informative, as shown by the example in Figure
\ref{fig:promo}(middle). Clearly, both good alignment, as well
as sufficient training images are needed to ensure success of the sparsity-based
recognition method proposed by \cite{Wright2009-PAMI}.
%Unfortunately, most public face databases lack images with a
%significant component of rear (more than 90 degrees from
%frontal) illumination, either for training or testing.
In this paper, we examine how to handle alignment and illumination simultaneously
in the sparse representation framework, bringing the method proposed in \cite{Wright2009-PAMI}
closer to practical use.

\subsection{Related Work}
We briefly review existing techniques for recognition, image
registration, and handling of illumination variation.  Our
system is based purely on 2D techniques.  This fact immediately
distinguishes our approach from systems that either require a
3D data as an input, or attempt to estimate a 3D model from 2D
input \cite{amberg2007reconstructing,Blanz2003-PAMI}.  While
these techniques can achieve better robustness to pose
variation given a sufficiently accurate 3D model, for access
control applications where only moderate pose variation is
present, the proposed method will be more than sufficient.
Note that 2D images of faces under varying illuminations
already contain 3D shape-related information,\footnote{In
principle, one can recover the 3D shape of the face from
multiple illuminations using photometric stereo.} and this
information can be leveraged by 2D algorithms for alignment and
recognition even if shape is not reconstructed explicitly.
%In addition, the proposed sparsity-based robust
%alignment and recognition techniques are not limited to 2D data and can be easily extended
%to 3D data if necessary.

@@

\begin{figure}
\centering
{\small
\begin{tabular}{cccc}
\includegraphics[height=.8in]{figures_cvpr/L1_cropped} &
\includegraphics[height=.8in]{figures_cvpr/y_warp_L1} &
\includegraphics[height=.8in]{figures_cvpr/y_hat_L1} &
\includegraphics[height=.8in]{figures_cvpr/e_L1} \\
\includegraphics[height=.8in]{figures_cvpr/L2_cropped} &
\includegraphics[height=.8in]{figures_cvpr/y_warp_L2} &
\includegraphics[height=.8in]{figures_cvpr/y_hat_L2} &
\includegraphics[height=.8in]{figures_cvpr/e_L2} \\
(a) & (b) & (c) & (d)
\end{tabular}
\vspace{0mm}}
\caption{{\bf Comparing alignment of a subject wearing sunglasses by
$\ell^1$ and $\ell^2$ minimization.}
{\bf Top:} alignment result of minimizing $\|\e\|_1$; {\bf Bottom:}
result of minimizing $\|\e\|_2$. (a) {\em Green (dotted):} Initial face boundary
given by the face detector, {\em Red (solid):} Alignment result shown on the same
face; (b) warped testing image using the estimated transformation $\y_0$;
(c) reconstructed face $A_i\x$ using the training; (d) image of error $\e$. }\label{fig:L1-L2-align}
\vspace{0mm}
\end{figure}

@@

\begin{algorithm}[thb]
\caption{\bf (Deformable Sparse Recovery and Classification for
Face Recognition)} \label{alg:deformable-src}
\begin{algorithmic}[1]
\begin{small}
\STATE {\bf Input:} Training images $\{A_i \in \Re^{m\times n_i}\}_{i=1}^K$ for $K$ subjects,  a test image
$\y\in\Re^m$ and a deformation group $T$.
\STATE
{\bf for} each subject $i$,
\STATE \hspace{3mm} $\tau^{(0)}
\leftarrow I$.
\STATE \hspace{3mm} {\bf while} not converged $(j=1,2,\ldots)$ {\bf do}
\STATE \hspace{6mm}
$\tilde \y(\tau) \leftarrow \frac{\y \circ \tau}{\|\y \circ
\tau\|_2}$; \;\;\; $J \leftarrow  \frac{\partial}{\partial
\tau} \tilde\y(\tau)  \bigr|_{\tau^{(j)}} $;
%\STATE \hspace{6mm} $(\hat \x, \hat \e, \Delta \tau) \leftarrow \left\{\begin{array}{l} \arg \min_{\x,\e,\Delta \tau} \| \e \|_1 \\  \subj \; \y + J \Delta \tau = A_k \x + \e \end{array}\right.$
\STATE \hspace{6mm} $ \Delta \tau =  \arg\min \; \| \e \|_1  \;
\subj \; \tilde \y + J \Delta \tau = A_i \x + \e.$
\STATE
\hspace{6mm} $\tau^{(j+1)} \leftarrow \tau^{(j)} + \Delta
\tau$;
\STATE \hspace{3mm} {\bf end while} \STATE {\bf end} \STATE Keep
the top $S$ candidates $k_1, \ldots, k_S$ with the smallest
residuals $\|\e\|_1$. \STATE Compute an average transformation
$\bar{\tau}$ from $\tau_{k_1}, \tau_{k_2}, \ldots, \tau_{k_S}$.
\STATE Update $\y \leftarrow \y \circ \bar{\tau}$ and $\tau_i
\leftarrow \tau_i \cdot \bar{\tau}^{-1}$ for $i = k_1, \dots,
k_S$. \STATE Set $A \leftarrow \big[ A_{k_1} \circ
\tau_{k_1}^{-1} \mid A_{k_2} \circ \tau_{k_2}^{-1} \mid \dots
\mid A_{k_S} \circ \tau_{k_S}^{-1} \big]$. \STATE Solve the
$\ell^1$-minimization problem: \hspace{2mm}
$\hat{\x} = \arg \min_{\x, \e} \| \x \|_1 + \|\e\|_1 \;\; \subj \;\; \y = A \x + \e.$
\STATE Compute residuals $r_i(\y) = \| {\y} - {A}_i \, \delta_i(\hat{\x}) \|_2$ for $i = k_1, \dots, k_S$.
\STATE {\bf Output:} $\mbox{identity}(\y) = \arg\min_i r_i(\y)$.
\end{small}
\end{algorithmic}
\end{algorithm}

@@

In order to discuss the solution to the above subproblems, we
need to define the following soft-thresholding operator for a
vector $\x$ and a scalar $\alpha \geq 0$:
\begin{equation}
\mathcal{T}(\x,\alpha) = \textup{sign}(\x)\cdot \max \{|\x| - \alpha, 0\},
\end{equation}
where all the operations are performed component-wise. It is
easy to show that the subproblem with respect to $\e$ has a
closed-form solution given by the soft-thresholding operator:
\begin{equation}
\e_{k+1} = \mathcal{T}(\y - A\x_k + \mu^{-1}\blamda_k, \mu^{-1}).
\end{equation}
To solve the subproblem associated with $\x$, we
apply a first-order $\ell^1$-minimization method,
called \emph{fast iterative shrinkage-threshold algorithm}
(FISTA) \cite{BeckA2009}. The main idea of FISTA is to
iteratively minimize a quadratic approximation $Q(\x, \z)$ to
$L_{\mu} (\x,\e_{k+1},\blamda_k)$ around a point $\z$, which is
carefully chosen in order to achieve a good convergence
rate. We summarize the entire ALM
algorithm as Algorithm~\ref{alg:alm}, where $\gamma$ denotes the
largest eigenvalue of the matrix $A^TA$. For the choice of parameter $\mu$, we take the same strategy as
in \cite{YangJ2009-pp} and set $\mu = 2m / \|\y\|_1$.
\begin{algorithm}[t]
\caption{\bf (Augmented Lagrange Multiplier Method for Global
Recognition)}
\begin{algorithmic}[1]
\begin{small}
\STATE {\bf Input:} $\y \in \Re^m$, $A \in \Re^{m \times n}$,
$\x_1 = \mathbf{0}$, $\e_1 = \y$, $\blamda_1 =
\mathbf{0}$.
\WHILE{not converged ($k = 1,2,\ldots$)}
\STATE $\e_{k+1} = \mathcal{T}\left(\y - A\x_k +
\frac{1}{\mu}\blamda_k, \frac{1}{\mu}\right)$;
\STATE $t_1\leftarrow 1$, $\z_1 \leftarrow \x_k$, $\w_1 \leftarrow \x_k$;
\WHILE{not converged ($l = 1,2,\ldots$)}
\STATE $\w_{l+1} \leftarrow \mathcal{T}\left(\z_l +
\frac{1}{\gamma}A^T\left(\y - A\z_l - \e_{k+1} +
\frac{1}{\mu}\blamda_k\right), \frac{1}{\mu\gamma}\right)$;
\STATE $t_{l+1} \leftarrow \frac{1}{2}\left( 1 +
\sqrt{1+4t_l^2}\right)$;
\STATE $\z_{l+1} \leftarrow \w_{l+1} + \frac{t_l - 1}{t_{l+1}}(\w_{l+1} - \w_l)$;
\ENDWHILE
\STATE $\x_{k+1} \leftarrow \w_{l}$,  \; $\blamda_{k+1} \leftarrow \blamda_k + \mu (\y - A\x_{k+1} - \e_{k+1})$;
\ENDWHILE \STATE
{\bf Output:} $\x^* \leftarrow \x_k, \e^* \leftarrow \e_k$.
\end{small}
\end{algorithmic}
\label{alg:alm}
\end{algorithm}

@@

\subsection{Simulations and Experiments on Region of
Attraction} We will now present three experimental results
demonstrating the effectiveness of the individual alignment
procedure outlined in the previous section. They show the sufficiency of the
region of attraction, verify effectiveness of the multiscale extension,
and show stability to small pose variations.  We delay large-scale recognition experiments
to Sections \ref{sec:multipie} and \ref{sec:own-data}, after we
have discussed the issue of illumination in the next section.

@@

\section{Handling Practical Illumination Variation}\label{sec:illumination}
In the above section, we have made the assumption that the test image, although taken under some arbitrary illumination, can be linearly represented by a finite number of training illuminations.  Under what conditions is this a reasonable assumption to make?  What can we say from first principles about how the training images should be chosen?

@@

\subsection{Improving the Performance by Choosing Different Sampling Windows}
Our algorithm's errors are mostly caused by a few subjects who
significantly change their appearances between sessions (such
as hair, facial hair, and eyeglasses). Some representative
examples are shown in Figure \ref{fig:failed-examples}. For those subjects, alignment and recognition fail on
almost all test illuminations.

@@

\vspace{-.1in}
\section{Tests on Our Own Database}\label{sec:own-data} Using the training acquisition
system we described in Section \ref{sec:illumination}, and shown in Figure
\ref{fig:system}, we have collected the frontal view of 109
subjects {\em without eyeglasses} under 38 illuminations shown
in Figure \ref{fig:illumination-patterns}. For testing our
algorithm, we have also taken 935 images of these subjects with
a different camera under a variety of practical conditions.

\vspace{-.1in}
\subsection{Necessity of Rear Illuminations} To see how
training illuminations affect the performance of our algorithm
in practice, we now compare how well a few frontal
illuminations can linearly represent: 1. other frontal illuminations
taken under the same laboratory conditions, and 2. typical
indoor and outdoor illuminations. To this end, we use the face
database acquired by our system and use 7 illuminations per
subject as training. The illuminations are chosen to be similar
to the 7 illuminations used in the previous experiment on
Multi-PIE.\footnote{We use the illuminations $\{6, 9, 12,
13, 18, 21, 22\}$ shown in Figure
\ref{fig:illumination-patterns}(b) to mimic the illuminations
 $\{0, 1, 6, 7, 13, 14, 18\}$ in Multi-PIE.} We then test
our algorithm on the remaining $24 - 7 = 17$ frontal
illuminations for all the subjects. The recognition rate is
$99.8\%$, nearly perfect. We also test our algorithm on 310
indoor images and 168 outdoor images of these subjects taken
under a variety of lighting conditions (category 1 and 2
specified below), similar to the one shown in Figure
\ref{fig:promo}, and the recognition rates for indoor and
outdoor images drop down to $94.2\%$ and $89.2\%$,
respectively. This is a strong indication that
frontal illuminations taken under laboratory conditions
are insufficient for representing test images under typical indoor and
outdoor illuminations.
\vspace{-0.1in}

>>>>

@@

\IEEEdisplaynotcompsoctitleabstractindextext
\vspace{-9mm} % HACK

@@

\begin{figure}
\centering \begin{tabular}{cc}
\includegraphics[height=1in]{figures_cvpr/promo/case1/detector.png}&
\hspace{3mm}
\includegraphics[height=1in]{figures_cvpr/promo/case1/sci_with_axis_face_case1.png}
\\ \includegraphics[height=1in]{figures_cvpr/promo/alignment_and_detector.png}&
\hspace{3mm}
\includegraphics[height=1in]{figures_cvpr/promo/case2/sci_with_axis_face_case2.png}
\\ \includegraphics[height=1in]{figures_cvpr/promo/case3/alignment.png} &
\hspace{3mm}
\includegraphics[height=1in]{figures_cvpr/promo/case3/sci_with_axis_face_case3.png}
\end{tabular} \caption{{\bf Effects of registration and illumination on
Recognition}. In this example we identify the girl among 20 subjects, by
computing the sparse representation of her input face with respect to the
entire training set. The absolute sum of the coefficients associated with each
subject is plotted on the right. We also show the faces reconstructed with each
subject's training images weighted by the associated sparse coefficients. The
red line (cross) corresponds to her true identity, subject 12. {\bf Top:} The
input face is from Viola and Jones' face detector (the black box) and all 38
illuminations specified in Section \ref{sec:illumination} are used in the
training.  {\bf Middle:} The input face is well-aligned (the white box) with
the training by our algorithm specified in Section \ref{sec:registration} but
only 24 frontal illuminations are used in the training for recognition (see
Section \ref{sec:illumination}). {\bf Bottom:} The input face is well aligned and
a sufficient set (all 38) of
illuminations are used in the training. Both are necessary for correct recognition
using SRC.}\label{fig:promo}
\vspace{-6.9mm}
\end{figure}

Unfortunately, while the work \cite{Wright2009-PAMI} achieves impressive results, it does not deal with misalignment
between the test and training images, and it requires a rich set of illuminations
in the gallery images for good performance.
We illustrate the compounded effect of both alignment and illumination
with an example in Figure \ref{fig:promo}.
The task is to identify the girl among 20 subjects. If the test
face image, say obtained from an off-the-shelf face detector,
has even a small amount of registration error against the
training images (caused by mild pose, scale, or misalignment),
the sparse representation obtained using the method of \cite{Wright2009-PAMI} is no longer informative,
even if sufficient illuminations are present in the training, as shown in Figure
\ref{fig:promo}(top). Additionally, in order to span
the illuminations of a typical indoor (or outdoor) environment,
illuminations from behind the subject are needed in the
training set. Otherwise, even for perfectly aligned test images,
the sparse representation obtained using \cite{Wright2009-PAMI} will not necessarily be sparse or
informative, as shown by the example in Figure
\ref{fig:promo}(middle). Clearly, both good alignment, as well
as sufficient training images are needed to ensure success of the sparsity-based
recognition method proposed by \cite{Wright2009-PAMI}.
In this paper, we examine how to handle alignment and illumination simultaneously
in the sparse representation framework, bringing the method proposed in \cite{Wright2009-PAMI}
closer to practical use.

\vspace{-0mm}
\subsection{Related Work}
We briefly review existing techniques for recognition, image
registration, and handling of illumination variation.  Our
system is based purely on 2D techniques.  This fact immediately
distinguishes our approach from systems that either require a
3D data as an input, or attempt to estimate a 3D model from 2D
input \cite{amberg2007reconstructing,Blanz2003-PAMI}.  While
these techniques can achieve better robustness to pose
variation given a sufficiently accurate 3D model, for access
control applications where only moderate pose variation is
present, the proposed method will be more than sufficient.
Note that 2D images of faces under varying illuminations
already contain 3D shape-related information,\footnote{In
principle, one can recover the 3D shape of the face from
multiple illuminations using photometric stereo.} and this
information can be leveraged by 2D algorithms for alignment and
recognition even if shape is not reconstructed explicitly.

@@

\begin{figure}
\centering
{\small
\begin{tabular}{cccc}
\includegraphics[height=.8in]{figures_cvpr/L1_cropped} &
\includegraphics[height=.8in]{figures_cvpr/y_warp_L1} &
\includegraphics[height=.8in]{figures_cvpr/y_hat_L1} &
\includegraphics[height=.8in]{figures_cvpr/e_L1} \\
\includegraphics[height=.8in]{figures_cvpr/L2_cropped} &
\includegraphics[height=.8in]{figures_cvpr/y_warp_L2} &
\includegraphics[height=.8in]{figures_cvpr/y_hat_L2} &
\includegraphics[height=.8in]{figures_cvpr/e_L2} \\
(a) & (b) & (c) & (d)
\end{tabular}
\vspace{0mm}}
\caption{{\bf Comparing alignment of a subject wearing sunglasses by
$\ell^1$ and $\ell^2$ minimization.}
{\bf Top:} alignment result of minimizing $\|\e\|_1$; {\bf Bottom:}
result of minimizing $\|\e\|_2$. (a) {\em Green (dotted):} Initial face boundary
given by the face detector, {\em Red (solid):} Alignment result shown on the same
face; (b) warped testing image using the estimated transformation $\y_0$;
(c) reconstructed face $A_i\x$ using the training; (d) image of error $\e$. }\label{fig:L1-L2-align}
\vspace{-8.0mm}
\end{figure}

@@

\begin{algorithm}[thb]
\caption{\bf (Deformable Sparse Recovery and Classification for
Face Recognition)} \label{alg:deformable-src}
\begin{algorithmic}[1]
\begin{small}
\STATE {\bf Input:} Training images $\{A_i \in \Re^{m\times n_i}\}_{i=1}^K$ for $K$ subjects,  a test image
$\y\in\Re^m$ and a deformation group $T$.
\STATE
{\bf for} each subject $i$,
\STATE \hspace{3mm} $\tau^{(0)}
\leftarrow I$.
\STATE \hspace{3mm} {\bf while} not converged $(j=1,2,\ldots)$ {\bf do}
\STATE \hspace{6mm}
$\tilde \y(\tau) \leftarrow \frac{\y \circ \tau}{\|\y \circ
\tau\|_2}$; \;\;\; $J \leftarrow  \frac{\partial}{\partial
\tau} \tilde\y(\tau)  \bigr|_{\tau^{(j)}} $;
%\STATE \hspace{6mm} $(\hat \x, \hat \e, \Delta \tau) \leftarrow \left\{\begin{array}{l} \arg \min_{\x,\e,\Delta \tau} \| \e \|_1 \\  \subj \; \y + J \Delta \tau = A_k \x + \e \end{array}\right.$
\STATE \hspace{6mm} $ \Delta \tau =  \arg\min \; \| \e \|_1  \;
\subj \; \tilde \y + J \Delta \tau = A_i \x + \e.$
\STATE
\hspace{6mm} $\tau^{(j+1)} \leftarrow \tau^{(j)} + \Delta
\tau$;
\STATE \hspace{3mm} {\bf end while} \STATE {\bf end} \STATE Keep
the top $S$ candidates $k_1, \ldots, k_S$ with the smallest
residuals $\|\e\|_1$. \STATE Compute an average transformation
$\bar{\tau}$ from $\tau_{k_1}, \tau_{k_2}, \ldots, \tau_{k_S}$.
\STATE Update $\y \leftarrow \y \circ \bar{\tau}$ and $\tau_i
\leftarrow \tau_i \cdot \bar{\tau}^{-1}$ for $i = k_1, \dots,
k_S$. \STATE Set $A \leftarrow \big[ A_{k_1} \circ
\tau_{k_1}^{-1} \mid A_{k_2} \circ \tau_{k_2}^{-1} \mid \dots
\mid A_{k_S} \circ \tau_{k_S}^{-1} \big]$. \STATE Solve the
$\ell^1$-minimization problem: \hspace{2mm}
$\hat{\x} = \arg \min_{\x, \e} \| \x \|_1 + \|\e\|_1 \;\; \subj \;\; \y = A \x + \e.$
\STATE Compute residuals $r_i(\y) = \| {\y} - {A}_i \, \delta_i(\hat{\x}) \|_2$ for $i = k_1, \dots, k_S$.
\STATE {\bf Output:} $\mbox{identity}(\y) = \arg\min_i r_i(\y)$.
\end{small}
\end{algorithmic}
\end{algorithm}
%\vspace{-4mm}

@@

In order to discuss the solution to the above subproblems, we
need to define the following soft-thresholding operator for a
vector $\x$ and a scalar $\alpha \geq 0$:
\begin{equation}
\mathcal{T}(\x,\alpha) = \textup{sign}(\x)\cdot \max \{|\x| - \alpha, 0\},
\end{equation}
where all the operations are performed component-wise. It is
easy to show that the subproblem with respect to $\e$ has a
closed-form solution given by the soft-thresholding operator:
\begin{equation}
\e_{k+1} = \mathcal{T}(\y - A\x_k + \mu^{-1}\blamda_k, \mu^{-1}).
\end{equation}
To solve the subproblem associated with $\x$, we
apply a first-order $\ell^1$-minimization method,
called \emph{fast iterative shrinkage-threshold algorithm}
(FISTA) \cite{BeckA2009}. The main idea of FISTA is to
iteratively minimize a quadratic approximation $Q(\x, \z)$ to
$L_{\mu} (\x,\e_{k+1},\blamda_k)$ around a point $\z$, which is
carefully chosen in order to achieve a good convergence
rate. We summarize the entire ALM
algorithm as Algorithm~\ref{alg:alm}, where $\gamma$ denotes the
largest eigenvalue of the matrix $A^TA$. For the choice of parameter $\mu$, we take the same strategy as
in \cite{YangJ2009-pp} and set $\mu = 2m / \|\y\|_1$.
\begin{algorithm}[t]
\caption{\bf (Augmented Lagrange Multiplier Method for Global
Recognition)}
\begin{algorithmic}[1]
\begin{small}
\STATE {\bf Input:} $\y \in \Re^m$, $A \in \Re^{m \times n}$,
$\x_1 = \mathbf{0}$, $\e_1 = \y$, $\blamda_1 =
\mathbf{0}$.
\WHILE{not converged ($k = 1,2,\ldots$)}
\STATE $\e_{k+1} = \mathcal{T}\left(\y - A\x_k +
\frac{1}{\mu}\blamda_k, \frac{1}{\mu}\right)$;
\STATE $t_1\leftarrow 1$, $\z_1 \leftarrow \x_k$, $\w_1 \leftarrow \x_k$;
\WHILE{not converged ($l = 1,2,\ldots$)}
\STATE $\w_{l+1} \leftarrow \mathcal{T}\left(\z_l +
\frac{1}{\gamma}A^T\left(\y - A\z_l - \e_{k+1} +
\frac{1}{\mu}\blamda_k\right), \frac{1}{\mu\gamma}\right)$;
\STATE $t_{l+1} \leftarrow \frac{1}{2}\left( 1 +
\sqrt{1+4t_l^2}\right)$;
\STATE $\z_{l+1} \leftarrow \w_{l+1} + \frac{t_l - 1}{t_{l+1}}(\w_{l+1} - \w_l)$;
\ENDWHILE
\STATE $\x_{k+1} \leftarrow \w_{l}$,  \; $\blamda_{k+1} \leftarrow \blamda_k + \mu (\y - A\x_{k+1} - \e_{k+1})$;
\ENDWHILE \STATE
{\bf Output:} $\x^* \leftarrow \x_k, \e^* \leftarrow \e_k$.
\end{small}
\end{algorithmic}
\label{alg:alm}
%\vspace{-4mm}
\end{algorithm}

@@

\subsection{Experiments on Region of Attraction} We will now present three
experimental results demonstrating the effectiveness of the individual
alignment procedure outlined in the previous section. They show the sufficiency
of the region of attraction, verify effectiveness of the multiscale extension,
and show stability to small pose variations.  We delay large-scale recognition
experiments to Sections \ref{sec:multipie} and \ref{sec:own-data}, after we
have discussed the issue of illumination in the next section.

@@

\section{Handling Illumination Variation}\label{sec:illumination}
In the above section, we have made the assumption that the test image, although taken under some arbitrary illumination, can be linearly represented by a finite number of training illuminations.  Under what conditions is this a reasonable assumption to make?  What can we say from first principles about how the training images should be chosen?

@@

\subsection{Improving the Sampling Window}
Our algorithm's errors are mostly caused by a few subjects who
significantly change their appearances between sessions (such
as hair, facial hair, and eyeglasses). Some representative
examples are shown in Figure \ref{fig:failed-examples}. For those subjects, alignment and recognition fail on
almost all test illuminations.

@@

%\vspace{-.1in}
\section{Tests on Our Own Database}\label{sec:own-data} Using the training acquisition
system we described in Section \ref{sec:illumination}, and shown in Figure
\ref{fig:system}, we have collected the frontal view of 109
subjects {\em without eyeglasses} under 38 illuminations shown
in Figure \ref{fig:illumination-patterns}. For testing our
algorithm, we have also taken 935 images of these subjects with
a different camera under a variety of practical conditions.
\vspace{-.1in}

\subsection{Necessity of Rear Illuminations} To see how
training illuminations affect the performance of our algorithm
in practice, we now compare how well a few frontal
illuminations can linearly represent: 1. other frontal illuminations
taken under the same laboratory conditions, and 2. typical
indoor and outdoor illuminations. To this end, we use the face
database acquired by our system and use 7 illuminations per
subject as training. The illuminations are chosen to be similar
to the 7 illuminations used in the previous experiment on
Multi-PIE.\footnote{We use the illuminations $\{6, 9, 12,
13, 18, 21, 22\}$ shown in Figure
\ref{fig:illumination-patterns}(b) to mimic the illuminations
 $\{0, 1, 6, 7, 13, 14, 18\}$ in Multi-PIE.} We then test
our algorithm on the remaining $24 - 7 = 17$ frontal
illuminations for all the subjects. The recognition rate is
$99.8\%$, nearly perfect. We also test our algorithm on 310
indoor images and 168 outdoor images of these subjects taken
under a variety of lighting conditions (category 1 and 2
specified below), similar to the one shown in Figure
\ref{fig:promo}, and the recognition rates for indoor and
outdoor images drop down to $94.2\%$ and $89.2\%$,
respectively. This is a strong indication that
frontal illuminations taken under laboratory conditions
are insufficient for representing test images under typical indoor and
outdoor illuminations.
\vspace{-0.1in}
